Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-10-21 reviews.Rmd
Update reviews.Rmd
Co-authored-by: Andreas Brandmaier <brandmaier@mpib-berlin.mpg.de>

Concerning Daniel Laken's review, we took the liberty to provide a high level summary of his main points because they are repeated across different subdiscussions throughout his letter.
We took special care to change the manuscript in response to his summary of suggestions (RC \@ref(pt:change-start) to RC \@ref(pt:change-end)).

>>>>

Concerning Daniel Laken's review, we took the liberty to provide a high level summary of his main points because they are repeated across different subdiscussions throughout his letter.
We are grateful for his comments and revised the manuscript in response to his summary of suggestions (RC \@ref(pt:change-start) to RC \@ref(pt:change-end)).
